### 2024-01-25 parts/transducers.tex
adding conjectures

>>>>

\begin{lemma}
    \label{trivial-for-unary:lemma}
    Let $f \in \NPoly$ having unary input.
    In particular, $f$ is commutative.
    Then, $f \in \NSF$ if and only if 
    the \kl{residual transducer} of $f$
    is \kl{counter-free}.
\end{lemma}
\begin{proof}
    If there is a counter... well we will find it ^^
\end{proof}

\begin{conjecture}
    If $f$ is commutative, and the \kl{residual transducer}
    has a counter, then it has a single letter counter.
\end{conjecture}

\begin{conjecture}
    If $f$ is commutative, then 
    $f \in \NSF$ if and only if the \kl{residual transducer}
    of $f$ is \kl{counter-free}.
\end{conjecture}
